---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geisha <img src='man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
<!-- badges: end -->

*geisha* is an R data package that provides the expression dataset from the
Gallus Expression in Situ Hybridization Analysis
([GEISHA](http://geisha.arizona.edu/geisha/about.jsp)) project.

The data here provided is of June 2, 2021, 12:29 AM. You can check whether this is
the latest version by visiting
[http://geisha.arizona.edu/geisha/downloads.jsp](http://geisha.arizona.edu/geisha/downloads.jsp).

## Installation

You can install the current version of geisha with:

```r
# install.packages("remotes")
remotes::install_github("ramiromagno/geisha")
```

## Usage

This package provides one single dataset: `geisha_expression`.

```{r example}
library(geisha)

geisha_expression
```

Each row refers to a gene found to be expressed in the chick embryo at a
specific Hamilton-Hamburger stage (`stage`) and anatomical location (`tissue`),
obtained from a specific source (indicated by the `geisha_id`).

Please note that the `stage` variable is a factor whose levels are: `r knitr::combine_words(levels(geisha_expression$stage))`, following
[Hamilton-Hamburger stage
series](https://anatomypubs.onlinelibrary.wiley.com/doi/abs/10.1002/aja.1001950405)
of chick embryos.

## Data source

The original data source is obtained from the GEISHA
[Downloads](http://geisha.arizona.edu/geisha/downloads.jsp) page.

## Citing this work

Please visit the [About GEISHA](http://geisha.arizona.edu/geisha/about.jsp) page
for citation details.
