---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(geisha)
```

# geisha <img src='man/figures/logo.svg' align="right" height="139" />

<!-- badges: start -->
<!-- badges: end -->

`{geisha}` is an R data package that provides the expression dataset from the
Gallus Expression in Situ Hybridization Analysis
([GEISHA](http://geisha.arizona.edu/geisha/about.jsp)) project.

The data here provided is of `r last_updates$date[1]`. You can check whether this is
the latest version by visiting
[http://geisha.arizona.edu/geisha/downloads.jsp](http://geisha.arizona.edu/geisha/downloads.jsp).

## Installation

You can install the current version of geisha with:

```r
# install.packages("remotes")
remotes::install_github("ramiromagno/geisha")
```

## Usage

At this moment this package provides only two datasets: `expression_txt` and `expression_xml`.

### Dataset `expression_txt`

```{r example}
library(geisha)

expression_txt
```

Each row refers to a gene found to be expressed in the chick embryo at a
specific set of Hamilton-Hamburger stages (`stages`) and anatomical locations (`locations`),
obtained from a specific source (indicated by the `geisha_id`).

Please note that the columns `stages` and `locations` are list-columns.

### Dataset `expression_xml`

Contrary to `expression_txt` that only lists the stages and the locations when/where a
gene is found expressed, in the object `expression_xml` you can actually know
the relationship between `stage` and `location`, i.e., which stages associate
with which locations.

```{r example2}
expression_xml
```

## Data source

The original data source is obtained from the GEISHA
[Downloads](http://geisha.arizona.edu/geisha/downloads.jsp) page.

## Citing this work

Please visit the [About GEISHA](http://geisha.arizona.edu/geisha/about.jsp) page
for citation details.
